\documentclass[10pt]{article}%
\author{Joshua N Grant}
\title{Invention Disclosures for Joshua N. Grant}
\date{\today{}}
\usepackage{palatino}
\usepackage{pifont}
\usepackage{enumitem}
\usepackage{sectsty}
\usepackage{fontawesome}
\hypersetup{colorlinks=true}
%\addbibresource{bibliography.bib}
\bibliographystyle{plain}
\usetikzlibrary{positioning,shapes,shadows,arrows,backgrounds,calc,shadows.blur}
%\setlength{\parindent}{0pt}
\sectionfont{\fontsize{10}{11}\selectfont}
\begin{document}
\maketitle
\section{Software}
\pragraph{Intro} Software projects in which I own the intellectual property..
\begin{itemize}
  \item \texttt{pyCWW} - python - a GUI to perform cell morphology analysis over a set of micrographs.
  \item \texttt{choppy} - python - a zonal statistical calculator for shapefiles + rasters, netCDF, etc. 
  \item \texttt{FinalFantasyFootball} - python/sql/docker/bash/R/html/css/JavaScript/kubernetes/spark/go - a distributed system for constant monitoring of webpages and APIs, updating a webpage with AI-derived semantic analysis.
  \item \texttt{znanje} - python/sql/docker/bash/kubernetes/go/html/css/JavaScript - a web 3 distributed posting system. Servers can be self-hosted, shared, or published, with each published post is encoded for streaming to the interface of the webrowser or client application.
  \item \texttt{python-wiki-cli} - python - a CLI interface to the wikipedia API/web
  \item \texttt{python-chatgpt-cli} - python - a CLI interface to Chat-GPT
  \item \texttt{python-dummy-db} - python/sql - generation of dummy data for databases.
  \item \texttt{ricing} - python/sql/docker/bash - control, save, backup, and manage configurations for various programs.
  \item \texttt{skeletons} - python/bash - quickly develop and deploy prototype projects.
  \item \texttt{god} - python/c++ - a game in which a user speaks, and that audio is converted into an entire universe. As the universe unfolds, a user can make other declarations which affects the behavior of the universe.
  \item \texttt{ThisIsACasino} - python/R/scala/c++/go - an algotrading bot and model that uses semantic analysis and TensorFlow models to perform trades of stocks, coins, and NFTs.
  \item \texttt{depy} - python - abstractions to requests, selenium, and psycopg2 to make development easier.
  \item \texttt{ccdp} - python - cookie cutter docker projects to quickly dockerize your applications.
  \item \texttt{mine} - R - collection of useful R functions and code.
  \item \texttt{archpy} - python - a CLI to recursively backup a folder
  \item \texttt{spektrah} - python/c++ - a blockchain technology centered around peer-reviewed authorship integrity.
  \item \texttt{phasedna} - python/R/\latex - create beautiful data-centric reports and graphics quickly.
  \item \texttt{PostDTW} - c - a Postgres plugin to calculate dynamic time warps.
\end{itemize}
\section{Literature}
\paragraph{Intro} A list of music and literature I have developed.
\begin{itemize}
  \item Thundershine - a high-fantasy that reveals it is hard science fiction.
  \item Heartwood - an alternative-history horror western set in the late 1800s.
  \item An Exchange of Nutrients - 300 million years in the future, the dominant life-form on the planet is a fungus, and this is its story.
\end{itemize}
\section{Music}
\paragraph{Intro} A list of music
\begin{itemize}
  \item Nobody \& the Everybody Else - an experimental trio focusing on low-fi electronic fusion.
  \item jng - independent musical efforts are released under this artist.
\end{itemize}
\end{document}
